---
title: "Univeristy of Washington GPA Report"
author: "Nicholas Xu"
date: "11/08/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F)
source("./boxplot_chart.R")
source("./summary.R")
```
## Introduction

This study is an exciting topic regarding UW courses and potentially could reach a lot of student’s demographics. A lot of students go to sites like ratemyprofessor.com or UW’s course evaluation to learn more about the courses before they commit. Therefore, the scarcity of the information circulating leads to considerable demand for such insights. By visualizing the avg GPA of UW courses, students can better assess the difficulties of each class they are taking. It also helps to foster transparency across college courses and would help us to make informed decisions to choose the right schedule for us.

## Summary

## Table

## Charts
### Chart #3 - GPA distribution across info200 class
This graph shows the gpa distribution of each letter grades from all professors of the class. The reason
to include this graph is that it explains the grading disparity across sections. For example,
the majority of the Chapin's class earned A, while very few students from Freeman's class earned an A.
Using stacked bar chart we can clearly see some professor gives eaiser grades on the class, 
while others are tougher. There is no other graph can present this information clearly.

```{r}
final_plot
```

